### 2019-08-14 README.Rmd
made small changes to the paper

@@

- work on first draft of paper
- read through papers giving an overview of the current explanation methods

>>>>

*First draft of paper due two weeks into the semester (Tuesday, September 10)*

@@

- keep the LIME procedure at a higher level in the paper
- check for ridge regression model in Python code
- compute generalized $R^2$ for my images
- change to computing the $\mathcal{L}$ metric from the paper
- check if Python package outputs the locality metric
- add figure descriptions in both caption and text
- go back through LIME procedure and update with new understanding (such as d' can be larger than d)
- add an assert_that statement in the code to check if the LIME package is changing
- read through papers giving an overview of the current explanation methods
